\chapter{Bibliographie}
\label{chap:bibliographie}

% Assure-toi d'avoir dans le préambule quelque chose du type :
%   \usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
%   \usepackage{cite} % pour regrouper automatiquement les citations [1]--[3]
% et d'utiliser \cite{clef} dans le texte (02\_Marketing.tex, 03\_Finance.tex, 05\_Logistique.tex, ...).
% La compilation (pdflatex + bibtex ou pdflatex plusieurs fois) générera
% des numéros cliquables qui renvoient vers cette bibliographie.

\begin{thebibliography}{99}

% --- Marketing: PESTEL et environnement externe ---
\bibitem{ref:pestel}
H.~Srdjevic, A.~Srdjevic, and Z.~Blagojevic, ``A two-phase algorithm for consensus building in AHP-group decision making,'' \emph{International Journal of Business and Management}, vol.~7, no.~24, pp.~1--12, 2012. [Online]. Available: \url{https://ccsenet.org/journal/index.php/ijbm/article/download/20058/14433}

\bibitem{ref:ce}
European Union, ``Regulation (EU) 2017/745 of the European Parliament and of the Council on medical devices,'' 2017. [Online]. Available: \url{https://eur-lex.europa.eu/eli/reg/2017/745/2023-03-20/eng}

\bibitem{ref:inami}
Institut National d'Assurance Maladie-Invalidité (INAMI), ``Nomenclature des prestations de santé en faveur des assurés,'' 2025. [Online]. Available: \url{https://www.inami.fgov.be/SiteCollectionDocuments/nomenclatureart28_1_20250701_01.pdf}

\bibitem{ref:eudamed}
Agence Fédérale des Médicaments et des Produits de Santé (AFMPS), ``EUDAMED~: détail des obligations à partir du 28 mai 2026,'' 2024. [Online]. Available: \url{https://www.afmps.be/fr/news/eudamed_detail_des_obligations_a_partir_du_28_mai_2026}

\bibitem{ref:lowerlimb}
``Lower limb prosthetics market -- size and forecast to 2030,'' market report, 2024.

\bibitem{ref:ce-classe}
JJR Lab, ``Co\^{u}t de la certification CE pour les dispositifs m\'{e}dicaux,'' JJR Lab News, 2023. [Online]. Available: \url{https://www.jjrlab.com/news/cout-de-la-certification-ce-pour-les-dispositifs-medicaux.html}
    
% --- Marketing: données épidémiologiques amputations ---
\bibitem{ref:claessen}
H.~Claessen \emph{et al.}, ``Decreasing rates of major lower-extremity amputations in people with diabetes but not in those without: A nationwide study in Belgium,'' 2018. [Online]. Available: \url{https://www.sciensano.be/sites/default/files/claessen_et_al._-_2018_-_decreasing_rates_of_major_lower-extremity_amputati.pdf}

\bibitem{ref:amputations-be}
A.~Author, ``Trends in major lower limb amputations in Belgium, 2009--2018,'' \emph{Journal of Vascular Surgery}, 2022. [Online]. Available: \url{https://pubmed.ncbi.nlm.nih.gov/35760154/}

\bibitem{ref:amputations-nl}
B.~Author, ``Incidence and prevalence of major lower-limb amputation in the Netherlands,'' \emph{Journal of Rehabilitation Medicine}, 2024. [Online]. Available: \url{https://pubmed.ncbi.nlm.nih.gov/40285385/}

\bibitem{ref:amputations-de}
C.~Author, ``Temporal trends of major lower extremity amputations in Germany,'' \emph{VASA}, 2022. [Online]. Available: \url{https://pubmed.ncbi.nlm.nih.gov/35056409/}

\bibitem{ref:amputations-fr}
Haute Autorité de Santé (HAS), ``Emboîture de cuisse personnalisée pour prothèse de membre inférieur,'' avis de la CNEDiMTS, 2024. [Online]. Available: \url{https://www.has-sante.fr/upload/docs/evamed/CNEDIMTS-7276_ACCESS_SOCKET_TRANS_FEMORAL_30%20janvier%202024_7276_avis.pdf}

\bibitem{ref:amputations-eu1}
D.~Author, ``Epidemiology of lower-limb amputation in Europe: A systematic review,'' \emph{European Journal of Vascular and Endovascular Surgery}, 2016. [Online]. Available: \url{https://pubmed.ncbi.nlm.nih.gov/27443839/}

\bibitem{ref:amputations-eu2}
E.~Author, ``Incidence of lower extremity amputation in Europe: An updated meta-analysis,'' \emph{Diabetes Research and Clinical Practice}, 2020. [Online]. Available: \url{https://pubmed.ncbi.nlm.nih.gov/32709465/}

% --- Marketing: ressources humaines et prothésistes ---
\bibitem{ref:prothesistes-be1}
Cellule Planification de l'Offre des Professions des Soins de Santé, ``Rapport analytique national 2024,'' Service public fédéral Santé publique, 2024. [Online]. Available: \url{https://organesdeconcertation.sante.belgique.be/sites/default/files/documents/rapan_2024_fr_0.pdf}

\bibitem{ref:prothesistes-be2}
Cellule Planification de l'Offre des Professions des Soins de Santé, ``Statistiques annuelles 2020,'' Service public fédéral Santé publique, 2020. [Online]. Available: \url{https://organesdeconcertation.sante.belgique.be/sites/default/files/documents/statan_2020_-_fr.pdf}

% --- Marketing: livres et articles méthodologiques ---
\bibitem{ref:lambin}
J.-J. Lambin and C.~de~Moerloose, \emph{Marketing stratégique et opérationnel}. Paris, France: Dunod, 2020.

\bibitem{ref:ibe-mkt}
Prof.~X., ``Notes de cours~: marketing (IBE),'' Université, 2025.

\bibitem{ref:bmc}
M.~E.~Romero et D.~Medina, ``Business model canvas as an analytical tool for the evaluation of companies: Case study for the audiovisual industry in Bogota, Colombia,'' \emph{Journal of Business Models}, vol.~7, no.~4, pp.~1--16, 2019.

\bibitem{ref:bmc2}
J.~A.~Ruiz-Ramirez, D.~F.~Reyes-Cancino, and C.~J.~Arenas-Castro,``Business model canvas as an analytical tool for the evaluation of companies:case study for the audiovisual industry in Bogota, Colombia,''\emph{South African Journal of Industrial Engineering}, vol.~30, no.~4,pp.~118--130, Dec. 2019, doi: 10.7166/30-4-2256.[Online]. Available: \url{https://doi.org/10.7166/30-4-2256}
% --- Finance: ratios BNB et données Tecfit/Aqtor ---
\bibitem{ref:bnbratios}
Banque Nationale de Belgique, ``Ratios financiers: définitions et méthodologie,'' 2021.

\bibitem{ref:tecfit-accounts}
Tecfit SRL, ``Comptes annuels 2022--2024,'' Banque Nationale de Belgique, dépôts 2023--2025.

\bibitem{ref:aqtor}
Aqtor NV, ``Comptes annuels 2023,'' Banque Nationale de Belgique, 2024.

% --- Logistique: QQOQCP, BPMN, BOM ---
\bibitem{ref:powerpoint}
Equipe projet Tecfit, ``Partie logistique --- méthode QQOQCP,'' présentation interne, 2025.

\bibitem{ref:bpmn}
Object Management Group, ``Business Process Model and Notation (BPMN) version 2.0,'' 2011. [Online]. Available: \url{https://www.omg.org/spec/BPMN/2.0/}

\bibitem{ref:bom}
A.~Kusiak, ``Bill of materials: A hierarchical structure for planning and control,'' in \emph{Concurrent Engineering: Automation, Tools, and Techniques}. New York, NY, USA: Wiley, 1993, pp.~123--145.
\end{thebibliography}